---
title: "p8105_Tidy Text"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidytext)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Get Data

```{r, cache=TRUE}
read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}

url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_reviews = 
  tibble(
    page = 1:100,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest(reviews) %>%
  mutate(review_num = row_number()) %>% 
  relocate(page, review_num)

```

## Do some tidy text stuff

```{r}
dynamite_words =
    dynamite_reviews %>% 
    unnest_tokens(word, text) %>% 
    select(-urls)
```

remove boring words

```{r}
dynamite_words =
    anti_join(dynamite_words, stop_words)
```

Usual Tidyverse stuff...

```{r}
dynamite_words %>% 
    count(word, sort = TRUE) %>% 
    top_n(10) %>% 
    mutate(word = fct_reorder(word, n)) %>% 
    ggplot(aes(x = word, y = n)) +
    geom_bar(stat = "identity") +
    coord_flip()
```

## Compare across groups

Groups I want to compare are 1 star ad 5 star reviews.

Let's count words in group.

```{r}
dynamite_words %>% 
    filter(stars %in% c(1, 5)) %>% 
    group_by(stars) %>% 
    count(word) %>% 
    top_n(5) %>% 
    knitr::kable()
```

```{r}
dynamite_words %>% 
    filter(stars %in% c(1, 5)) %>% 
    group_by(stars) %>% 
    summarise(n = n()) %>% 
    knitr::kable()
```

We now need an "odds ratio"

```{r}
word_ratios = 
    dynamite_words %>% 
    filter(stars %in% c(1, 5)) %>% 
    count(word, stars) %>% 
    group_by(word) %>% 
    filter(sum(n) >= 5) %>% 
    ungroup(word) %>% 
    pivot_wider(
        names_from = stars, 
        values_from = n,
        names_prefix = "stars_", 
        values_fill = 0
    ) %>% 
    mutate(
        stars_1_odds = (stars_1 + 1) / (sum(stars_1) + 1), 
        stars_5_odds = (stars_5 + 1) / (sum(stars_5) + 1), 
        log_OR = log(stars_5_odds / stars_1_odds)
    )
```

Can we do something useful with this?

```{r}
word_ratios %>% 
    mutate(pos_log_OR = ifelse(log_OR > 0, "5 stars > 1 star", 
                               "1 star > 5 stars")) %>% 
    group_by(pos_log_OR) %>% 
    top_n(10, abs(log_OR)) %>% 
    ungroup() %>% 
    mutate(word = fct_reorder(word, log_OR)) %>% 
    ggplot(aes(x = word, y = log_OR, fill = pos_log_OR)) +
    geom_bar(stat = "identity") + 
    coord_flip()
```

## Sentiment analysis

Load lexicon

```{r}
bing_sentiments = get_sentiments("bing")
```

Get sentiments for dynamite reviews.

```{r}
dynamite_sentiments =
    inner_join(dynamite_words, bing_sentiments) %>% 
    count(review_num, sentiment) %>% 
    pivot_wider(
        names_from = sentiment, 
        values_from = n, 
        values_fill = 0
    ) %>% 
    mutate(
        review_sentiment = positive - negative
    ) %>% 
    select(review_num, review_sentiment)
```
Combine with full data

```{r}
dynamite_sentiments =
    left_join(dynamite_sentiments, dynamite_reviews) %>% 
    select(-urls)
```

```{r}
dynamite_sentiments %>% 
    mutate(
        review_num = factor(review_num), 
        review_num = fct_reorder(review_num, review_sentiment)) %>% 
    ggplot(aes(x = review_num, y = review_sentiment, 
               fill = stars)) +
    geom_bar(stat = "identity") +
    theme(
        axis.title.x = element_blank(), 
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()
        )
```

Can we look at positive and negative reviews?

```{r}
dynamite_sentiments %>% 
    filter(review_sentiment == max(review_sentiment)) %>% 
    pull(text)
```

